---
title: "Guessing mean velocities expansion game!"
author: "Developing Data Products Course Project"
date: "27 Jul 2014"
output: html_document
---

This is an game! :D
Your goal is to guess the expansion velocity of the galaxies.

### Data
The data used in this game comes from MASS library of R package.
The data is a vector of velocities in km/sec of 82 galaxies from 6 well-separated conic sections of an unfilled survey of the Corona Borealis region.
```{r data1}
library(MASS); data(galaxies); str(galaxies)
```

You can get more information typing the next chunk in R:
```{r data2}
help(galaxies)
```
### How can I play?
It's really simple. Yo should to use the side bar in left region of the screen in order to **guess the mean expansion velocity** of the galaxies given in mentioned data.

### How I know if I get good results?
Well, you can use:

- Data histogram (try to get the solution with only this graphic)
- Given values of
      - Difference between your value and real value
      - RMSE root mean square error commited
- Data set graphic information

```{r graph}
par(mfrow=c(1,2))
hist(galaxies, xlab='velocity (km/sec)', col='orange',
     main='Histogram respresentation', cex.lab=1.1, cex.main=1.2)
lines(c(mean(galaxies),mean(galaxies)), c(0, 46), col="green",lwd=5)
plot(galaxies, ylab='Velocity (km/sec)', xlab="Each one of the given galaxies in data set",
     col="orange", pch=8, lwd=3, main='Data set representation', cex.lab=1.1, cex.main=1.2)
lines(x=c(0,length(galaxies)),y=c(mean(galaxies),mean(galaxies)), col="green",lwd=5)
```

NOTE: solution is represented by green line in each of previous graphs. During the game, your selected MU will be showed in red color.


> Remember, you want to minimize RMSE value ;)

### How does it work?
It's simple. You enter a value through slider bar, this will be your MU value (NOTE: MU is your try mean value).
Then, app plot your given value in the histrogram giving you:

- DIFFERENCE: The difference between your value (MU) and the real value (the solution)
- RMSE: The RMSE root mean square error comminted in your MU selection.

#### How app calculate this values?

- Difference is calculated by: $DIFFERENCE = MU - mean(galaxies)$
- RMSE is calculated by: $RMSE = sqrt(mean((galaxies - mu)^2))$

> Do not worry about calculation, just try it!!! :D

### What is the goal of the game?

You should to reduce DIFFERENCE and RMSE. So, best value in both cases will be 0.

 -It is really hard to get it with the slide bar :D

> That's the game ;) :D

### I hope you enjoy it!
